### 2016-06-28 paper/introduction.tex
added in abstract draft and contribution list

\bcp{May I reiterate my request to put all the text and figures into one big
.tex file?  Makes finding things, global replace, renaming sections, etc. very much easier.  :-)}

@@

>>>>

@@

KEY INSIGHTS
\begin{enumerate}
\item Search through all possible lenses by: searching for good regular
expressions, then searching within those regular expressions for type directed
lenses
\item Putting the regular expressions in a normal form reduces the number of
regular expressions we must search through
\item Using user defined data types allows the synthesis algorithm to keep the
internals of regular expressions abstracted, unless the internals of those
regular expressions are changed, and the abstraction must be broken.
\item Using a pseudometric on regular expressions, based on the
distribution of user defined data types and size of the regular expression,
allows for an efficient search through equivalent regular expressions
\item We use a data structure combining examples with regular expressions to
synthesize only candidate programs which obey the examples
\item We develop an efficient strategy for finding if two
regular expressions have a lens between them requiring no rewrites which amounts
to merely ordering the components.
\end{enumerate}
